\chapter{Evaluation}
%TC:ignore
\begin{comment}

Examiners expect to find a section addressing questions such as:

\begin{itemize}
   \item Were the requirements correctly identified? 
   \item Were the design decisions correct?
   \item Could a more suitable set of tools have been chosen?
   \item How well did the software meet the needs of those who were expecting to use it?
   \item How well were any other project aims achieved?
   \item If you were starting again, what would you do differently?
\end{itemize}

Other questions can be addressed as appropriate for a project. 

Such material is regarded as an important part of your work; it should demonstrate that you are capable not only of carrying out a piece of work but also of thinking critically about how you did it and how you might have done it better. This is seen as an important part of an honours degree. 

There will be good things and room for improvement with any project. As you write this section, identify and discuss the parts of the work that went well and also consider ways in which the work could be improved. 

In the latter stages of the module, we will discuss the evaluation. That will probably be around week 9, although that differs each year. 
\end{comment}
%TC:endignore
\section{Requirements}

Requirments are unclear. More bakcground research needed to begin with.


\section{Design, Implementation and Tools}

The design decisions worked well as the code was produced to a good standard that is very flexible. It could accommodate future Projects around the topic.


Tool selection was suitable. the tools were iterated upon during the project as needs changed due to the agile nature of the research project.

The software meets the needs of those who were expecting to use it, with both a simple UI for a front end user or for demo purposes and a easy to use object-oriented programming interface for technical users.

\section{Project Aims}

The aim of the project to explore using images to count sheep, this goal was achieved even if the methods selected were not the most suitable.


\section{Self evaluation}

\subsection{What did I do right?}

Agile methodology

Wrote report in \LaTeX, saved so much time formating images.

Flexible interfaces for the project.

\subsection{What did I do wrong?}

TESTING TESTING TESTING

error handling, currently just print anything

Communicate better with contacts provided

\subsection{What would I do differently?}

Not have a global pandemic?

Do more initial research.

More emphasis on testing, make plan at start.

Research error handling for the projects language at start.

