\documentclass[11pt,a4paper]{report}
\usepackage{StylesAndReferences/mmp-report}

\usepackage{cite}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pdfpages}

\definecolor{mmpTitle}{RGB}{0,96,15}
\definecolor{mmpSection}{RGB}{56,142,60}
\definecolor{mmpSubsection}{RGB}{106,191,105}

\chapterfont{\color{mmpTitle}}  % sets colour of chapters
\sectionfont{\color{mmpSection}}  % sets colour of sections 
\subsectionfont{\color{mmpSubsection}} % sets colour subsections
\subsubsectionfont{\color{mmpSubsection}} % sets colour subsections

\reporttype{Agile}

\begin{document}

%TC:ignore

\pagenumbering{roman}

% This is the front page
\include{FrontMatter/cover}                        

% Set up page numbering
\pagestyle{empty}

% declarations of originality 
\include{FrontMatter/declaration}               

\include{FrontMatter/acknowledgements} % Acknowledgements

\include{FrontMatter/abstract}                 % Abstract

\include{FrontMatter/glossary}  

\pagenumbering{roman}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0 pt}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}

\tableofcontents   
\newpage
\listoffigures % comment out this line if you don't have any figures / graphics
\newpage 
\listoftables % comment out this line if you don't have any tables
\newpage

% Set up page numbering
\pagenumbering{arabic}

\setchapterheaderfooter

%TC:endignore

% include the chapters
%\include{Chapters_Agile/1background}
%\include{Chapters_Agile/2method}
%\include{Chapters_Agile/3sprint1}
%\include{Chapters_Agile/3sprint2}
%\include{Chapters_Agile/3sprint3}
%\include{Chapters_Agile/4results}
%\include{Chapters_Agile/5evaluation}
\include{Chapters_Research/1background}
\include{Chapters_Research/2method}
\include{Chapters_Research/3software}
\include{Chapters_Research/4results}
\include{Chapters_Research/5evaluation}
% add any additional chapters here

%TC:ignore
\setemptyheader

\nocite{*} % include everything from the bibliography, irrespective of whether it has been referenced.

% the following line is included so that the bibliography is also shown in the table of contents. There is the possibility that this is added to the previous page for the bibliography. To address this, a newline is added so that it appears on the first page for the bibliography. 
\addcontentsline{toc}{chapter}{Annotated Bibliography} % Adds References to contents page

%
% example of including an annotated bibliography. The current style is an author date one. If you want to change, comment out the line and uncomment the subsequent line. You should also modify the packages included at the top (see the notes earlier in the file) and then trash your aux files and re-run. 
%\bibliographystyle{StylesAndReferences/authordate2annot}
\bibliographystyle{StylesAndReferences/IEEEannotU}
\renewcommand{\bibname}{Annotated Bibliography} 

\bibliography{StylesAndReferences/mmp} % References file


\setemptyheader

\addcontentsline{toc}{chapter}{Appendices}
\chapter*{Appendices}
\begin{comment}
The appendices are for additional content that is useful to support the discussion in the report. It is material that is not necessarily needed in the body of the report, but its inclusion in the appendices makes it easy to access. 

For example, if you have developed a Design Specification document as part of a plan-driven approach for the project, then it would be appropriate to include that document as an appendix. In the body of your report you would highlight the most interesting aspects of the design, referring your reader to the full specification for further detail.

If you have taken an agile approach to developing the project, then you may be less likely to have developed a full requirements specification. Perhaps you use stories to keep track of the functionality and the 'future conversations'. It might not be relevant to include all of those in the body of your report. Instead, you might include those in an appendix. 

There is a balance to be struck between what is relevant to include in the body of your report and whether additional supporting evidence is appropriate in the appendices. Speak to your supervisor or the module coordinator if you have questions about this.
\end{comment}
\pagebreak

% start the appendix - sets up different numbering
\fancypagestyle{plain}{%
%\fancyhf{} % clear all header and footer fields
\fancyhead[L]{Appendix\ \thechapter}
\fancyhead[R]{\leftmark}}

\appendix
\fancyhead[L]{Appendix\ \thechapter}
\fancyhead[R]{\leftmark}
\fancyhead[C]{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}

\fancyhead[L]{Appendix\ \thechapter}
\fancyhead[R]{\leftmark}
\fancyfoot[C]{{\thepage} of \pageref{LastPage}}

% include any appendices here
\include{Appendices/appendixA}
\include{Appendices/appendixB}
\include{Appendices/appendixC}
\include{Appendices/appendixD}
\include{Appendices/appendixE}

\fancypagestyle{plain}{%
   \fancyhead{} %[C]{Annotated Bibliography}
   \fancyfoot[C]{{\thepage} of \pageref{LastPage}} % except the center
   \renewcommand{\headrulewidth}{0pt}
   \renewcommand{\footrulewidth}{0pt}
}

%TC:endignore

\end{document}
